---
title: "project_lesson 5"
author: "Pramil Jain"
output: html_document
---

# Create a histogram of diamond prices.
# Facet the histogram by diamond color
# and use cut to color the histogram bars.

```{r}

ggplot(diamonds, aes(x = price, fill = cut)) +
  geom_histogram() +
  facet_wrap(~ color)

ggsave("hist_diamond_price_facetColor_coloerCut.png")

```

# Create a scatterplot of diamond price vs.
# table and color the points by the cut of
# the diamond.

```{r}

ggplot(diamonds, aes(x = table, y = price, color = cut)) + 
  geom_jitter(size = 5) +
  scale_color_brewer(type = 'qual')+
  scale_x_continuous(breaks = seq(50, 80, 2))
  
ggsave("price_table_coloerCut.png")

```

# Create a scatterplot of diamond price vs.
# volume (x * y * z) and color the points by
# the clarity of diamonds. Use scale on the y-axis
# to take the log10 of price. You should also
# omit the top 1% of diamond volumes from the plot.


```{r}

ggplot(subset(diamonds, volume <= quantile(volume, 0.99) & volume > 0 ), aes(x = volume, y = price, color = clarity)) + 
  geom_jitter(size = 5) +
  scale_y_log10()+
    scale_color_brewer(type = 'div')
  
  
ggsave("volume_price_coloerClarity.png")

```

# Your task is to create a new variable called 'prop_initiated'
# in the Pseudo-Facebook data set. The variable should contain
# the proportion of friendships that the user initiated.

```{r}

glimpse(pf)

pf <- pf %>%
 mutate(prop_initiated = friendships_initiated/friend_count)

glimpse(pf)

pf <- pf %>%
mutate(prop_initiated = ifelse(friend_count > 0, friendships_initiated/friend_count, 0))

sample_n(pf,10)

```

# Create a line graph of the proportion of
# friendships initiated ('prop_initiated') vs.
# tenure and color the line segment by
# year_joined.bucket.

# Recall, we created year_joined.bucket in Lesson 5
# by first creating year_joined from the variable tenure.
# Then, we used the cut function on year_joined to create
# four bins or cohorts of users.

# (2004, 2009]
# (2009, 2011]
# (2011, 2012]
# (2012, 2014]


```{r}

pf <- pf %>%
  mutate(year_joined = floor(2014 - tenure/365),
         year_joined_bucket = cut(year_joined, breaks=c(2004, 2009, 2011, 2012, 2014))) 


ggplot(subset(pf, tenure > 0), aes(x=tenure, y=prop_initiated)) +
  geom_line(aes(color=year_joined_bucket), stat='summary', fun.y=mean) 

ggsave("tenure_prop_initiated_ColorYearBuck.png")

```

# Smooth the last plot you created of
# of prop_initiated vs tenure colored by
# year_joined.bucket. You can bin together ranges
# of tenure or add a smoother to the plot.

```{r}

ggplot(subset(pf, tenure > 0), aes(x=tenure, y=prop_initiated)) +
  
  geom_smooth(aes(color = year_joined_bucket))

ggsave("Smooth_tenure_prop_initiated_ColorYearBuck.png")

```



```{r}

pf %>%
  filter(year_joined_bucket == "(2012,2014]") %>%
  summarise(avg = mean(prop_initiated, na.rm=TRUE))

```

# Why do you think this group has highest freindship initiated 

# They have are new to fb, hence higher potential
# This group moght be more socially active

# Create a scatter plot of the price/carat ratio
# of diamonds. The variable x should be
# assigned to cut. The points should be colored
# by diamond color, and the plot should be
# faceted by clarity.

```{r}

ggplot(diamonds, aes(x = cut, y = price/carat, color = color)) + 
  geom_jitter() + 
  facet_wrap(~clarity)
  
ggsave("plot_price per catat_colorColor.png")

```






